\bf Faster Neural Machine Translation Inference

### 2018-02-06 fast-beam/fast-beam.tex
fast beam paper

We shall leave step 1 for future work and focus on the last three steps, the outline for which are shown in Algorithm~\ref{algo:original-softmax-beamsearch}. For brevity, we show the algorithm for 1-best, a beam search of the n-best is a simple extension of this.

@@

It has been shown ~\citep{koehn-knowles:2017:NMT} that using beam search to use the n-best number of classes, rather than just the best class, improves translation quality. This is a simple extension to the algorithm of Algorithm~\ref{algo:Fused Kernel}. Unlike the 1-best case, however, the softmax calculation cannot be skipped as the denominator differs for each input.

>>>>

We shall leave step 1 for future work and focus on the last three steps, the outline for which are shown in Algorithm~\ref{algo:original-softmax-beamsearch}. For brevity, we show the algorithm for 1-best, a beam search of the n-bests is a simple extension of this.

@@

It has been shown ~\citep{koehn-knowles:2017:NMT} that using beam search to use the n-best number of classes, rather than just the best class, improves translation quality, up to a point. Unlike the 1-best case, however, the softmax calculation cannot be skipped as the denominator differs for each input.
